### 2018-02-08 Sections/QTCP_protocol_stack.tex
Fixed graphic sizes, added stubs for QEC, added quantum Stockmarket, minor tweaks
Global spellcheck
Added grover search... started anyway
DFS encoding

\begin{figure}[!htb]\index{QTCP protocol stack}
\includegraphics[width=\columnwidth]{stack}
\caption{Protocol stack for QTCP. The protocol stack mediates communication of quantum data from Alice to Bob using the shown layers of abstraction. The end goal is to provide Bob a virtual interface to Alice's transmitted data, while remaining oblivious to the underlying protocol.} \label{fig:stack}\index{QTCP protocol stack}
\end{figure}

@@

@@

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{
function ThreeQubitCode($\ket\psi$):
\begin{enumerate}
\item Using two CNOT gates, redundantly encode the logical single-qubit state,
\begin{align}
\ket\psi=\alpha\ket{0}+\beta\ket{1},
\end{align}
into the three-qubit state,
\begin{align}
\ket\psi_R &= \hat{\text{CNOT}}_{1,2}\hat{\text{CNOT}}_{1,3}\ket\psi\ket{00} \nonumber \\
&= \alpha\ket{000}+\beta\ket{111}.
\end{align}
\item Independently apply bit-flip channels $\mathcal{E}_X$ to each of the three encoded qubits.
\item If exactly one bit-flip operation was applied in total, the three possible erroneous encoded states are,
\begin{align}
\ket\psi_1 &= \hat{X}_1 \ket\psi_R = \alpha\ket{001}+\beta\ket{110}, \nonumber \\
\ket\psi_2 &= \hat{X}_2 \ket\psi_R = \alpha\ket{010}+\beta\ket{101}, \nonumber \\
\ket\psi_3 &= \hat{X}_3 \ket\psi_R = \alpha\ket{100}+\beta\ket{011}.
\end{align}
\item Determine the parity of each of the three pairs of encoded qubits.
\item Assuming at most a single bit-flip operation has occurred on the encoded state, the three parity outcomes uniquely determine which encoded qubit the bit-flip was applied to.
\item Apply classically-controlled bit-flip recovery operations, $\mathcal{R}$, to correct the encoded state, recovering $\ket\psi_R$.
\item Apply the inverse of the encoding operation to recover $\ket\psi$.
\item $\Box$
\end{enumerate}}
\begin{align}
\Qcircuit @C=1.3em @R=.6em {
  & \lstick{\ket{\psi}} & \ctrl{2} & \gate{\mathcal{E}_X}  & \qw & \qw              & \ctrl{3}  & \qw       & \ctrl{4} & \qw & \multigate{2}{\ \mathcal{R}\ } & \qw \\
  & \lstick{\ket{0}}    & \targ    & \gate{\mathcal{E}_X}  & \qw & \qw              & \ctrl{2}  & \ctrl{2}  & \qw      & \qw & \ghost{\ \mathcal{R}\ } \qw & \qw \\
  & \lstick{\ket{0}}    & \targ    & \gate{\mathcal{E}_X}  & \qw & \qw              & \qw       & \ctrl{2}  & \ctrl{3} & \qw & \ghost{\ \mathcal{R}\ } \qw & \qw \\
  &          &          &          & & \lstick{\ket{0}} & \targ \qw & \qw       & \qw      & \meter & \control \cw \cwx \\
  &          &          &          & & \lstick{\ket{0}} & \qw       & \targ \qw & \qw      & \meter & \control \cw \cwx \\
  &          &          &          & & \lstick{\ket{0}} & \qw       & \qw       & \targ    & \meter & \control \cw \cwx
} \nonumber
\end{align}
}}
\caption{3-qubit code for protecting against at most a single logical bit-flip error. The doubly-controlled CNOT gates represent parity measurements, \mbox{$n_3=n_1\oplus n_2$}, where $n_i$ represents the value of the $i$th qubit. In a Hadamard-rotated basis, the same circuit may be employed to protect against a single phase-flip error. And by concatenating the two we obtain a 9-qubit code protecting against a single depolarising error (i.e joint bit-flip/phase-flip), which is a universal single-qubit error model.} \label{alg:three_QEC}
\end{table}

>>>>

\begin{figure}[!htb]\index{QTCP protocol stack}
\includegraphics[width=0.47\textwidth]{stack}
\caption{Protocol stack for QTCP. The protocol stack mediates communication of quantum data from Alice to Bob using the shown layers of abstraction. The end goal is to provide Bob a virtual interface to Alice's transmitted data, while remaining oblivious to the underlying protocol.} \label{fig:stack}\index{QTCP protocol stack}
\end{figure}

@@

\comment{Summary here. Shift bulk to QOS chapter.}

@@

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{
function ThreeQubitCode($\ket\psi$):
\begin{enumerate}
\item Using two CNOT gates, redundantly encode the logical single-qubit state,
\begin{align}
\ket\psi=\alpha\ket{0}+\beta\ket{1},
\end{align}
into the 3-qubit state,
\begin{align}
\ket\psi_R &= \hat{\text{CNOT}}_{1,2}\hat{\text{CNOT}}_{1,3}\ket\psi\ket{00} \nonumber \\
&= \alpha\ket{000}+\beta\ket{111}.
\end{align}
\item Independently apply bit-flip channels $\mathcal{E}_X$ to each of the three encoded qubits.
\item If exactly one bit-flip operation was applied in total, the three possible erroneous encoded states are,
\begin{align}
\ket\psi_1 &= \hat{X}_1 \ket\psi_R = \alpha\ket{001}+\beta\ket{110}, \nonumber \\
\ket\psi_2 &= \hat{X}_2 \ket\psi_R = \alpha\ket{010}+\beta\ket{101}, \nonumber \\
\ket\psi_3 &= \hat{X}_3 \ket\psi_R = \alpha\ket{100}+\beta\ket{011}.
\end{align}
\item Determine the parity of each of the three pairs of encoded qubits.
\item Assuming at most a single bit-flip operation has occurred on the encoded state, the three parity outcomes uniquely determine which encoded qubit the bit-flip was applied to.
\item Apply classically-controlled bit-flip recovery operations, $\mathcal{R}$, to correct the encoded state, recovering $\ket\psi_R$.
\item Apply the inverse of the encoding operation to recover $\ket\psi$.
\item $\Box$
\end{enumerate}}
\begin{align}
\Qcircuit @C=1.3em @R=.6em {
  & \lstick{\ket{\psi}} & \ctrl{2} & \gate{\mathcal{E}_X}  & \qw & \qw              & \ctrl{3}  & \qw       & \ctrl{4} & \qw & \multigate{2}{\ \mathcal{R}\ } & \qw \\
  & \lstick{\ket{0}}    & \targ    & \gate{\mathcal{E}_X}  & \qw & \qw              & \ctrl{2}  & \ctrl{2}  & \qw      & \qw & \ghost{\ \mathcal{R}\ } \qw & \qw \\
  & \lstick{\ket{0}}    & \targ    & \gate{\mathcal{E}_X}  & \qw & \qw              & \qw       & \ctrl{2}  & \ctrl{3} & \qw & \ghost{\ \mathcal{R}\ } \qw & \qw \\
  &          &          &          & & \lstick{\ket{0}} & \targ \qw & \qw       & \qw      & \meter & \control \cw \cwx \\
  &          &          &          & & \lstick{\ket{0}} & \qw       & \targ \qw & \qw      & \meter & \control \cw \cwx \\
  &          &          &          & & \lstick{\ket{0}} & \qw       & \qw       & \targ    & \meter & \control \cw \cwx
} \nonumber
\end{align}
}}
\caption{3-qubit code for protecting against at most a single logical bit-flip error. The doubly-controlled CNOT gates represent parity measurements, \mbox{$n_3=n_1\oplus n_2$}, where $n_i$ represents the value of the $i$th qubit. In a Hadamard-rotated basis, the same circuit may be employed to protect against a single phase-flip error. And by concatenating the two we obtain a 9-qubit code protecting against a single depolarising error (i.e joint bit-flip/phase-flip), which is a universal single-qubit error model. \comment{Move to QOS section}} \label{alg:three_QEC}
\end{table}

### 2018-02-08 Sections/about_the_authors.tex
Worked on security essay. Added Zixin.
DFS encoding

\comment{All photos must have same dimension (aspect ratio)}

@@

\includegraphics[width=\columnwidth]{photo_peter_rohde}

Peter Rohde is an ARC Future Fellow in the Centre for Quantum Software \& Information at the University of Technology Sydney (UTS:Q$|$SI$\rangle$), and associate member of the Hearne Institute for Theoretical Physics at Louisiana State University. He obtained a Bachelor of Computer Systems Engineering with First Class Honours, and a PhD in theoretical physics at the University of Queensland. He has worked at highly-acclaimed international institutes, including the University of Oxford, University of Queensland, Institute for Molecular Biosciences and Max-Planck Institute for the Science of Light, with over 45 publications and 1,200+ citations in quantum optics, quantum computing, quantum information theory and ecology. His theoretical proposals have inspired several world-leading experimental efforts, including time-bin encoded {\sc BosonSampling} and sub-shot-noise limited quantum metrology. In his spare time he is a musician, composer, public speaker, charity worker, mountaineer and adrenaline junkie. He regularly speaks at prominent scientific outreach events, features in newspaper and magazine articles, and conducts radio interviews. He is a very naughty boy and was expelled from preschool.

\includegraphics[width=\columnwidth]{photo_zuen_su}

@@

\includegraphics[width=\columnwidth]{photo_heliang_huang}

@@

@@

\includegraphics[width=\columnwidth]{photo_sihui_tan}

@@

\includegraphics[width=\columnwidth]{photo_nana_liu}

@@

\includegraphics[width=\columnwidth]{photo_ryan_mann}

@@

\includegraphics[width=\columnwidth]{photo_rohit_ramakrishnan}

@@

\includegraphics[width=\columnwidth]{photo_tim_byrnes}

@@

\includegraphics[width=\columnwidth]{photo_jon_dowling}

@@

\includegraphics[width=\columnwidth]{photo_bill_munro}

>>>>

\comment{All photos must have same dimension (aspect ratio = 1)}

@@

\begin{center}
\includegraphics[width=0.47\textwidth]{photo_peter_rohde}
\end{center}

Peter Rohde is an ARC Future Fellow in the Centre for Quantum Software \& Information at the University of Technology Sydney (UTS:Q$|$SI$\rangle$), and associate member of the Hearne Institute for Theoretical Physics at Louisiana State University. He obtained a Bachelor of Computer Systems Engineering with First Class Honours, and a PhD in theoretical physics at the University of Queensland. He has worked at highly-acclaimed international institutes, including the University of Oxford, University of Queensland, Institute for Molecular Biosciences and Max-Planck Institute for the Science of Light, with over 50 publications and 1,300+ citations in quantum optics, quantum computing, quantum information theory and ecology. His theoretical proposals have inspired several world-leading experimental efforts, including time-bin encoded {\sc BosonSampling} and sub-shot-noise limited quantum metrology. In his spare time he is a musician, composer, public speaker, charity worker, mountaineer and adrenaline junkie. He regularly speaks at prominent scientific outreach events, features in newspaper and magazine articles, and conducts radio interviews. He is a very naughty boy and was expelled from preschool.

\begin{center}
\includegraphics[width=0.47\textwidth]{photo_zuen_su}
\end{center}

@@

\begin{center}
\includegraphics[width=0.47\textwidth]{photo_heliang_huang}
\end{center}

@@

\begin{center}
\includegraphics[width=0.47\textwidth]{photo_zixin_huang}
\end{center}

Zixin Huang completed her PhD in physics at the University of Sydney, Australia. She is currently a postdoctoral fellow at the University of Sheffield, UK.

@@

\begin{center}
\includegraphics[width=0.47\textwidth]{photo_sihui_tan}
\end{center}

@@

\begin{center}
\includegraphics[width=0.47\textwidth]{photo_nana_liu}
\end{center}

@@

\begin{center}
\includegraphics[width=0.47\textwidth]{photo_ryan_mann}
\end{center}

@@

\begin{center}
\includegraphics[width=0.47\textwidth]{photo_rohit_ramakrishnan}
\end{center}

@@

\begin{center}
\includegraphics[width=0.47\textwidth]{photo_tim_byrnes}
\end{center}

@@

\begin{center}
\includegraphics[width=0.47\textwidth]{photo_jon_dowling}
\end{center}

@@

\comment{Complete this section}x

\begin{center}
\includegraphics[width=0.47\textwidth]{photo_bill_munro}
\end{center}

### 2018-02-08 Sections/quality_of_service.tex
Latin quote stubs
Very minor
DFS encoding

@@

%
% Topological codes
%

\subsection{Topological codes}\index{Topological codes}

%
% Topological Codes
%

@@

@@

>>>>

\comment{To do}
\comment{Syndrome extraction}\index{Syndrome extraction}

@@

\comment{These are a particular example of stabiliser codes with an elegant graphical interpretation}

\comment{Missing degree of freedom in stabilisers defines qubit. How does topology (genus) relate to number of logical qubits?}

@@

%
%
% Topological Codes
%

\comment{Toric code}

@@

%
% Decoherence-Free Subspaces
%

\subsection{Decoherence-free subspaces}\index{Decoherence-free subspaces}

The QoS techniques discussed previously were based on the notion of performing measurements on quantum systems to project them into subspaces devoid of errors. For example, in the 3-qubit code, measurement of the syndrome qubits projects the encoded state into a subspace where there was either no error, or in which an error occurred whose location is known and may therefore be corrected.

An alternate approach is to encode quantum information into Hilbert spaces which are invariant under a given error model. Such spaces are referred to as \textit{decoherence-free subspaces} (DFSs). In this instance we assume the error model is known, for example a dephasing channel, such that we can choose the appropriate DFS. To illustrate this idea we will consider encoding a single logical qubit into two physical qubits. The error model we will encode against is a collective $Z$-rotation, where the two physical qubits are subject to perfectly correlated $Z$ errors. This arises naturally in the context of, say, atomic qubits subject to the same external electromagnetic field, and therefore accumulate the associated phase errors in tandem.

A single-qubit $Z$-rotation of angle $\phi$ is given by $e^{i\phi\hat{Z}}$, which operates on logical basis states as,
\begin{align}
	e^{i\phi\hat{Z}} \ket{0} &\to \ket{0}, \nonumber \\
	e^{i\phi\hat{Z}} \ket{1} &\to e^{i\phi}\ket{1}.
\end{align}

Now we employ the encoding for logical basis states,
\begin{align}
\ket{0}_L &\equiv \ket{0}\ket{1},\nonumber \\
\ket{1}_L &\equiv \ket{1}\ket{0}.
\end{align}
Note that under a common $Z$-rotation, both logical basis states evolve identically by acquiring the same phase,
\begin{align}
	e^{i\phi\hat{Z}_1}e^{i\phi\hat{Z}_2}\ket{0}_L &= e^{i\phi}\ket{0}_L,\nonumber\\
	e^{i\phi\hat{Z}_1}e^{i\phi\hat{Z}_2}\ket{1}_L &= e^{i\phi}\ket{1}_L.
\end{align}
Thus, when acting on an arbitrary linear combination of these basis states (i.e a logical qubit),
\begin{align}
\ket\psi_L = \alpha \ket{0}_L + \beta\ket{1}_L,
\end{align}
the action of the error model is to acquire a global phase factor,
\begin{align}
	e^{i\phi\hat{Z}_1}e^{i\phi\hat{Z}_2} \ket\psi_L &= e^{i\phi}(\alpha\ket{0}_L + \beta\ket{1}_L) \nonumber \\
	&= e^{i\phi}\ket\psi_L,
\end{align}
which is physically irrelevant. This type of DFS encoding therefore protects a logical qubit against arbitrary correlated $Z$-rotations.

The same principle can be logically extended to many other correlated error models. For example, operating in a rotated basis (under a Hadamard transform), one could similarly protect against correlated $X$-rotations using the encoding,
\begin{align}
\ket{0}_L &\equiv \ket{-}\ket{+},\nonumber \\
\ket{1}_L &\equiv \ket{+}\ket{-},
\end{align}
where \mbox{$\ket\pm=\frac{1}{\sqrt{2}}(\ket{0}\pm\ket{1})$}.

One can conceptually think of the DFS encoding as being a type of `symmetry encoding', whereby the robustness against a particular error model arises due to the symmetry invariance of the action of the correlated errors on the encoded state. This idea, although very simple, is very powerful, since it is a completely passive form of error correction, requiring no syndrome measurements or correction operations. It also arises quite naturally in some systems where external fields act roughly uniformly across the physical qubits within a system.

%
% Dynamical Decoupling
%

\subsection{Dynamical decoupling}

\comment{To do, bang-bang, time-reversal}
